Holomorphic field theories and higher algebra

### 2023-08-18 highervertexops.tex
small edits while reading new stuff

\begin{prop}\label{prop:res}
The higher algebraic residue defines a cochain map
\beqn
\sfA \to \left(\sfA \, \d^2 z\right)^\vee [-1]
\eeqn 
which sends an element $a \in \sfA$ to the functional
\beqn
F_a \colon b \, \d^2 z \in \sfA\, \d^2 z \mapsto (-1)^{|a|} \Res(a b \, \d^2 z) .
\eeqn
\brian{weird sign, but I think it's there because of the $[-1]$ shift.}
When extended to the completed version of punctured affine space, this assignment defines an isomorphism of cochain complexes 
\beqn
F \colon \Hat\sfA \simeq \left(\Hat\sfA \, \d^2 z\right)^\vee [-1] .
\eeqn
\end{prop}
\begin{proof}
Suppose that $a \in \sfA^0$. 
Then
\begin{align*}
F_{\dbar a} (b \d^2 z) & = - \Res \left( (\dbar a) b \d^2 z \right) \\
& = - \Res\left( \dbar(a b \d^2 z) \right) + \Res \left(a \dbar b \d^2 z\right) \\
& = F_{a} (\dbar b \d^2 z) .
\end{align*}
In the final line we have used (3) from lemma \ref{lem:res}.
If $a \in \sfA^1$ then $F_{\dbar a}(b \d^2 z) = 0 = F_{a} (\dbar b \d^2 z)$ for all $b$.

@@

Consider the vector space $V = \laurent$.
Via the residue pairing we have an identification $V^\vee = \laurent \, \d^2 z [1]$, see proposition \ref{prop:res}.
From hereon we use the notation $\laurent^{(2)} = \laurent \, \d^2 z$.
We will denote linear elements in the corresponding Poisson algebra
\beqn
\cP = \Sym \left(\laurent  \oplus \laurent^{(2)}[1] \right) ,
\eeqn
by $(\sfb , \sfc)$.
On these elements, the Poisson bracket reads
\beqn
\{\sfb ,\sfc\} = \Res(\sfb \sfc) .
\eeqn
The Lie algebra $\cP_2$ is spanned by symbols of the form $\sfb \sfb',\sfb \sfc, \sfc \sfc'$ where $\sfb,\sfb'\in \laurent$ and $\sfc,\sfc' \in \laurent^{(2)}[1]$.

The algebra $\cP$ is the free commutative algebra generated by $\laurent \oplus \laurent^{(2)}[1]$.
Alternatively, we can view, via the residue pairing, a linear element $(\sfb, \sfc) \in \laurent \oplus \laurent^{(2)}[1]$ as the functional
\beqn
(\sfb, \sfc) \colon \laurent^{(2)} [1] \oplus \laurent \to \C
\eeqn
defined by
\beqn
(\beta, \gamma) \mapsto (-1)^{|\sfb|} \Res(\sfb \beta) + (-1)^{|\sfc|} \Res(\sfc \gamma) .
\eeqn
Likewise, we can view a quadratic element in $\cP_2$ as a functional
\beqn
\Sym^2 \left(\laurent^{(2)} [1] \oplus \laurent \right) \to \C .
\eeqn
For example, the quadratic element $\sfb \sfc \in \cP_2$ corresponds to the quadratic functional
\beqn
\beta \gamma \mapsto (-1)^{|\sfb|+ |\sfc|} \Res (\sfb \beta) \Res(\sfc \gamma) ,
\eeqn
where $\beta \in \laurent^{(2)} [1]$ and $\gamma \in \laurent$.

>>>>

\begin{prop}\label{prop:res}
The higher algebraic residue defines a cochain map
\beqn
\sfA \to \left(\sfA \, \d^2 z\right)^\vee [-1]
\eeqn 
that sends an element $a \in \sfA$ to the functional $F_a$ where 
\beqn
F_a(b \, \d^2 z) =  (-1)^{|a|} \Res(a b \, \d^2 z) .
\eeqn
\brian{weird sign, but I think it's there because of the $[-1]$ shift.}
When extended to the completed version of punctured affine space, this assignment defines an isomorphism of cochain complexes 
\beqn
F \colon \Hat\sfA \simeq \left(\Hat\sfA \, \d^2 z\right)^\vee [-1] .
\eeqn
\end{prop}

\begin{proof}
Suppose that $a \in \sfA^0$. 
Then
\begin{align*}
F_{\dbar a} (b\, \d^2 z) & = - \Res \left( (\dbar a) b \,\d^2 z \right) \\
& = - \Res\left( \dbar(a b \,\d^2 z) \right) + \Res \left(a \dbar b \,\d^2 z\right) \\
& = F_{a} (\dbar b \,\d^2 z) .
\end{align*}
In the final line we have used (3) from lemma \ref{lem:res}.
If $a \in \sfA^1$ then $F_{\dbar a}(b \,\d^2 z) = 0 = F_{a} (\dbar b \,\d^2 z)$ for all $b$.

@@

Consider the vector space $V = \laurent$.
Via the residue pairing we have an identification $V^\vee = \laurent \, \d^2 z [1]$ (see proposition \ref{prop:res}).
From hereon we use the notation $\laurent^{(2)} = \laurent \, \d^2 z$.
We will denote linear elements in the corresponding Poisson algebra
\beqn
\cP = \Sym \left(\laurent  \oplus \laurent^{(2)}[1] \right) ,
\eeqn
by $(\sfb , \sfc)$.
On these elements, the Poisson bracket reads
\beqn
\{\sfb ,\sfc\} = \Res(\sfb \sfc) .
\eeqn
The Lie algebra $\cP_2$ is spanned by symbols of the form $\sfb \sfb',\sfb \sfc, \sfc \sfc'$ where $\sfb,\sfb'\in \laurent$ and $\sfc,\sfc' \in \laurent^{(2)}[1]$.

The algebra $\cP$ is the free commutative algebra generated by $\laurent \oplus \laurent^{(2)}[1]$.
We can view, via the residue pairing, a linear element $(\sfb, \sfc) \in \laurent \oplus \laurent^{(2)}[1]$ as the linear functional
\[
\begin{array}{cccc}
(\sfb, \sfc) \colon & \laurent^{(2)} [1] \oplus \laurent & \to & \C\\
& (\beta, \gamma) & \mapsto  &(-1)^{|\sfb|} \Res(\sfb \beta) + (-1)^{|\sfc|} \Res(\sfc \gamma) .
\end{array}
\]
%\eeqn
%defined by
%\beqn
%(\beta, \gamma) \mapsto (-1)^{|\sfb|} \Res(\sfb \beta) + (-1)^{|\sfc|} \Res(\sfc \gamma) .
%\eeqn
Likewise, we can view a quadratic element in $\cP_2$ as a linear functional
\beqn
\Sym^2 \left(\laurent^{(2)} [1] \oplus \laurent \right) \to \C .
\eeqn
For example, the quadratic element $\sfb \sfc \in \cP_2$ corresponds to the quadratic functional
\beqn
\beta \gamma \mapsto (-1)^{|\sfb|+ |\sfc|} \Res (\sfb \beta) \Res(\sfc \gamma) ,
\eeqn
where $\beta \in \laurent^{(2)} [1]$ and $\gamma \in \laurent$.
